### 2023-12-22 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
rerendering docs

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scratch.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scratch_files/md-default1.js" type="text/javascript"></script><script src="scratch_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="scratch_files/vega3.js" type="text/javascript"></script><script src="scratch_files/vega4.js" type="text/javascript"></script><script src="scratch_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />

<div class="sourceClojure">
```clojure
(ns scratch
  (:require [scicloj.noj.v1.datasets
             :as datasets]
            [scicloj.noj.v1.vis.hanami
             :as hanami]
            [scicloj.kindly.v4.kind
             :as kind]))
```
</div>

# Intro

@@

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"scratch_files\/0.csv","format":{"type":"csv"}}});</script></div>

@@

<div><pre><small><small>source: projects/visual-tools/clay-calva-demo-20231216/notebooks/scratch.clj</small></small></pre></div>

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

# Clay & Noj demo: data visualization

<div class="sourceClojure">
```clojure
(ns index
  (:require [scicloj.noj.v1.datasets
             :as datasets]
            [scicloj.noj.v1.vis.hanami
             :as hanami]
            [scicloj.kindly.v4.kind
             :as kind]))
```
</div>

@@

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"index_files\/0.csv","format":{"type":"csv"}}});</script></div>

@@

<div><pre><small><small>source: projects/visual-tools/clay-calva-demo-20231216/notebooks/index.clj</small></small></pre></div>
